Something something progress in light

### 2022-08-03 2_SSL_EES/article/article_supplementary.tex
started adding content to main paper
added table to supplementary information

\documentclass{article}
% formatting
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
% cross-referencing
\usepackage{hyperref}
\usepackage{url}
\usepackage{doi}
% tables
\usepackage{booktabs}
% fonts
\usepackage{amsfonts}
\usepackage{microtype}
% figures
\usepackage{graphicx}
% math
\usepackage{amsmath}

% template
\usepackage{style_files/arxiv}

@@

\author{
    \href{https://orcid.org/0000-0003-4859-2650}
    {\includegraphics[scale=0.06]{2_SSL_EES/article/figures/orcid.pdf}
    \hspace{1mm}
    Michael Weinold} \\
	ETH Zurich\\
    Switzerland \\
	\texttt{michael.weinold@alumni.ethz.ch} \\
	\AND
	Dr. Sergey Kolesnikov\\
	University of Cambridge \\
	United Kingdom \\
    \And
	Laura Diaz Anadon \\
	University of Cambridge \\
	United Kingdom \\
}

@@

>>>>

\documentclass{article}
% formatting
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
% cross-referencing
\usepackage{hyperref}
\usepackage{url}
\usepackage{doi}
% tables
\usepackage{booktabs}
% fonts
\usepackage{amsfonts}
\usepackage{microtype}
% figures
\usepackage{graphicx}
% math
\usepackage{amsmath}
% tables
\usepackage{tabularx}
\usepackage{colortbl}
\definecolor{silver}{rgb}{0.75, 0.75, 0.75}

% template
\usepackage{auxiliary/arxiv_template_style_files/arxiv}

@@

\author{
    \href{https://orcid.org/0000-0003-4859-2650}
    {\includegraphics[scale=0.06]{2_SSL_EES/article/auxiliary/rsc_template_figures/orcid.pdf}
    \hspace{1mm}
    Michael Weinold} \\
	ETH Zurich\\
    Switzerland \\
	\texttt{michael.weinold@alumni.ethz.ch} \\
	\AND
	Dr. Sergey Kolesnikov\\
	University of Cambridge \\
	United Kingdom \\
    \And
	Laura Diaz Anadon \\
	University of Cambridge \\
	United Kingdom \\
}

@@

\section{Contribution of spillovers}

    \begin{table}[h!]
        \centering
    	\begin{tabularx}{\textwidth}{|l|l|X|X|X|X|}
    		\hline
    			Year & $\eta_L$[\%]  & $\Delta \eta_L^{abs}$[\%] & $\Delta \eta_L^{rel}$[\%]  & $\Delta \eta_L^{abs}(S/O)$[\%]  & $\Delta \eta_L^{rel}(S/O)$[\%]  \\
    		\hline
    			2002 & 5.8 & \multicolumn{4}{c|}{\cellcolor{silver}} \\
    		\hline
    		    \multicolumn{2}{|c|}{2002-2010} & 6.8 & 117.4 & 1.0 & 14.4 \\
    		\hline
    			2010 & 12.5 & \multicolumn{4}{c|}{\cellcolor{silver}} \\
    		\hline
    		    \multicolumn{2}{|c|}{2010-2016} & 19.9 & 158 & 1.6 & 8.0 \\
    		\hline
    			2016 & 32.5 & \multicolumn{4}{c|}{\cellcolor{silver}} \\
    		\hline
    		    \multicolumn{2}{|c|}{2016-2020} & 6.2 & 19.0 & 0.3 & 3.9 \\
    		\hline
    			2020 & 38.7 & \multicolumn{4}{c|}{\cellcolor{silver}} \\
    		\hline
    		    \multicolumn{2}{|c|}{2002-2020} & 32.9 & 566.4 & 2.8 & 8.5 \\
            \hline
    	\end{tabularx}
    	\caption{Contribution of technology spillovers to improvements in the total lamp efficiency $\eta_L$ for warm white light-emitting diodes in the period 2002-2020. Note numbers are rounded. \\ $\Delta \eta_L^{abs}\overset{eg.}{=}\eta_L(2010)-\eta_L(2002)$ is absolute change in total lamp efficiency. \\ $\Delta \eta_L^{rel}\overset{eg.}{=}(\eta_L(2010)-\eta_L(2002))/(\eta_L(2002)/100)$ is relative change in lamp efficiency.}
    	\label{tab:spillover-data}
    \end{table}
